Scrutinizing the linear variable importance of local explanations of non-linear models with animated linear projections

### 2021-12-29 _paper.rmd
-.mp4 of the case studies, - added mp4 url and embelishment to case studies. - need to validate that linkes work.

<!-- Paper structure -->
The remainder of this paper is organized as follows. The following section, [Local explanation statistics](#sec:explanations), covers the background of the local explanation, SHAP, and the traditional visuals produced from it. [Tours and the radial tour](#sec:tour) digs deeper into these animations of continuous linear projections. The section [Application Design](#sec:applicationdesign) discusses the visual layouts, how they facilitates analysis, data preprocessing, and package infrastructure. The section [Case Studies](#sec:casestudies) illustrates several applications of this method. We conclude with a [Discussion](#sec:cheemdiscussion) of the insights we draw from classification and regression tasks.

@@

<!-- Uses of local explanations -->
These instance-level explanations are used in various ways depending on the data. In images, saliency maps overlay or offset a heatmap indicating which pixels were necessary [@simonyan_deep_2014]. For instance, snow may be highlighted when distinguishing if a picture contains a wolf or husky. In text analysis, word-level contextual sentiment analysis can be used to highlight the sentiment and magnitude of influential words [@vanni_textual_2018]. In the case of numeric regression, they are used to explain variable additive contributions from the model intercept to the observation's prediction [@ribeiro_why_2016].

@@

<!-- Illustration -->
Figure \@ref(fig:shapdistrbd) shows the SHAP values of these players. Panel a) shows these players receive a sizable difference in wages. Panel b) shows the underlying distribution of the SHAP attributions while permuting the explanatory variables, with the medians being the SHAP values. In the light of the player position, the difference in the variable importance makes sense; offense and movement skills are more important for the offensive player, while defensive and power skills are more informative to the model for explaining the prediction of the defensive player. We would likewise expect the profile of variable importance to be unique for star players of other positions, such as goalkeepers or middle fielders. Panel b) shows a simplified break-down plot [@gosiewska_ibreakdown_2019], where a local explanation is used to additively explain the difference from the intercept to the observation's prediction. Such additive approaches will show asymmetry in the variable ordering, so we opt to fix the order to panel a), by decreasing sum of the SHAP values.

<!-- Segue -->
In summary, this figure highlights how local explanations bring interpretability to a model, at least in the vicinity of their observations. In this instance, two players with different positions receive different profiles of variable importance to explain the prediction of their wages. In application we apply _tree SHAP_, a variant of SHAP that enjoys a lower computational complexity [@lundberg_consistent_2018]. Tree SHAP only compatible with tree-based models; we illustrate on random forests. In the following section, we will use normalized explanations as the starting projection basis to further scrutinize the explanation.

@@

<!-- Manual tour -->
The manual tour [@cook_manual_1997] defines its basis path by manipulating a selected variable's basis contribution. A manipulation dimension is appended onto the projection plane, giving a full contribution to the chosen variable. The bases are then selected based on rotating this newly created manipulation space. A crucial feature of the manual tour is that it allows users to control the variable contributions of the basis. Such manipulations can be selected and queued in advance or selected on the spot for human-in-the-loop analysis [@karwowski_international_2006]. However, this navigation is relatively time-consuming due to the vast volume of the display-space. It is advisable to use this method to explore the sensitivity of the variable contribution to a previously identified feature of interest. In this case, the projection of the normalized explanations is the feature of interest.

@@

Below we illustrate the two primary displays of the cheem viewer application: the global view and the tour view. Then we cover what we take away from the classification and regression tasks. Lastly, we discuss the preprocessing the data before application runtime.

@@

<!-- Purpose -->
The global view provides an essential context of all observations and facilitates the exploration of the separability of the data- and attribution-spaces. While comparison of these spaces is interesting, the global view's purpose is to facilitate the selection of observations. The local explanation of these points will be explored in more detail.

<!-- Approximations of the spaces, PC1:2 -->
An approximation of these spaces is given as the first two principal components of their respective spaces. Model information, observed response by its prediction, is also provided. The orientation and magnitude of the variables are inscribed on a unit circle. <!-- Interactions -->Misclassified observations are circled in red if applicable. Linked brushing between the plots and tabular display of select points facilitates exploration of the spaces and the model. A single 2D projection will not encompass all of the structure of higher-dimensional space. However, it is a reasonable summarization given the real task at hand; the selection of observations to explore further.

@@

<!-- Tour animation -->
The radial tour creates a basis path by varying the contribution of a selected variable, fully into and out of a projection frame. Doing so tests an individual variable's sensitivity to the structure identified by the local explanation.The default variable selected has the largest discrepancy between the attribution of primary and comparison observations. The following sections elaborate on the takeaways we draw from applying this approach in classification and regression tasks, respectively. <!-- Segue to classification -->Now that we have introduced the global view and corresponding cheem radial tour let us discuss the differences between the classification and regression cases.

@@

What information do we glean from using this method on a classification task? Typically we select a misclassified observation compared to a correctly classified point nearby in data space. The initial frame is the linear attribution of that observation's local explanation. By default, the manual tour varies the contribution of the variable with the largest difference between the primary and comparison observation. That is, we can test the sensitivity of each variable to structure identified by the local explanation; we are exploring the support of the explanation, evaluating the support or robustness of the prediction.

```{r classificationcase, echo=F, out.width = "100%", fig.align="center", fig.cap = "Display illustrating the classification case. Plots are  colored on predicted class and red circles indicate misclassified observations. The radial tour is a 1D projection starting at the normalized tree SHAP values of the primary point. The first frame is the linear-variable importances that best describe the difference from model intercept to this observation's prediction. We probe the support of the variable contributions by selecting a variable to vary the contribution."}
knitr::include_graphics("./figures/app_classification.PNG")
```

@@

In the regression case, the global view can be colored on a statistic to highlight the structure in the explanation space, including residuals, log Mahalanobis distance of data space (a measure of outlyingness), and the correlation of the attribution projection with the observed response. In the radial tour, the horizontal positions are the same, the basis projection of the radial tour. The vertical position is fixed to the observed response variable and residuals in the middle and right panels, respectively. Correspondingly, the display changes from univariate density to 2D scatterplot. The basis is still one component (horizontal) independent of the vertical position.

```{r regressioncase, echo=F, out.width = "100%", fig.cap="Display of the regression task. The global view can be colored on the correlation of the attribution projection and observed response. In the tour, the horizontal values are the same as the classification case; the projection through the basis. The vertical position is now maped to the observed y and residuals."}
knitr::include_graphics("./figures/app_regression.PNG")
```

@@

<!-- Reactive vs exploration interactions -->
The application has several reactive inputs that affect the data used, aesthetic display, and tour manipulation. These reactive inputs make the software flexible and extensible. The application also has It also has more exploratory interactions to help link points in the data and extract other information not on plot axes.

@@

```{r interactions, echo=F, out.width = "100%", fig.cap = "Illustration of data explorations interactions in the global view. This view has linked brushing of the points where observations selected in one facet are highlighted in the other facets and populate an interactive tabular display below. Tooltips display when hovering over an obersvation."}
knitr::include_graphics("./figures/app_interactions.PNG")
```

@@

It is vital to mitigate the render time of visuals, especially when users may want to iterate many times. In order to keep render time low all of the computational operations should be prepared before runtime. The work remaining at runtime is solely reacting to inputs and rendering of visuals and tables. Below we discuss the steps and details of the reprocessing.

@@

<!-- Note on time of execution -->
The time to preprocess the data will vary significantly with the model and local explanation. For reference, the FIFA data, 5000 observations of nine explanatory variables, took 2.9 seconds to fit a random forest model of modest hyperparameters. Extracting the tree SHAP values of each observation took 254 seconds combined. PCA and statistics of the variables and attributions took 0.6 seconds. These runtimes were from a non-parallelized R session on a modern laptop, but suffice to say that the bulk of the time will be spent on the local attribution. An increased of model complexity or data dimensionality will quickly become an obstacle. This makes tree SHAP, with its reduced computational complexity, a good candidate to start with. Alternatively, the package __fastshap__ [@greenwell_fastshap_2020] claims extremely low runtimes, which are attributed to fewer calls to the prediction function, partial implementation in C++, and efficient use of logical subsetting.

@@

```{r casepenguins, echo=F, out.width = "100%", fig.cap = "Species classification of Palmer penguin data."}
knitr::include_graphics("./figures/case_penguins.png")
```

@@

The chocolates dataset consists of 88 observations of 10 nutritional measurements from their labels. Each of which was labeled as being either milk or dark chocolates. With this data, we can see if a manufacturer accurately portrays the chocolate. We are curious to see if there are chocolates that nutritionally look like milk chocolates labeled as dark chocolates, which may hold a higher market value. We should note that not all chocolates consist wholly of chocolate. The addition of other ingredients will decrease the predictive power of the model nutritional explanatory variable. A random forest model is fit classifying the type of chocolate. We selected a chocolate labeled dark, through predicted to be milk chocolate compared with a chocolate labeled 85% cocoa.

```{r casechocolates, echo=F, out.width = "100%", fig.cap = "Chocolates data type classification (milk or dark)."}
knitr::include_graphics("./figures/case_chocolates.png")
```

In figure \@ref(fig:casechocolates),  we similarly see that attribution space is more separable than data-space. Interestingly, the class imbalance that we suspected was not observed; there are only six chocolates labeled as dark and predicted as milk, while eight of the inverse case. Calories from fat is the variable with the largest difference in treeshap attribution between these points.

@@

```{r casefifa, echo=F, out.width = "100%", fig.cap = "FIFA 2020, regressing log wages [2020 Euros] from aggregations of skill measurements. The primary observation is a star offensive player (L. Messi) compared with a top defensive player (V. van Dijk)."}
knitr::include_graphics("./figures/case_fifa.png")
```

With figure \@ref(fig:casefifa), we will test the premise of the local explanation. If we remove reaction and movement skills from the basis, then offense skills have almost singular importance for explaining the offensive player. We vary the contribution of offensive skills. In the tour (panel b, frame 3), offensive skills are removed, and Messi is no longer separated from the group. We also notice that accuracy has rotated into the frame, maintaining some separability.

@@

```{r caseames, echo=F, out.width = "100%", fig.cap = "Ames housing 2018 regressing log sales price [2018 USD]."}
knitr::include_graphics("./figures/case_ames2018.png")
```

@@

The need to maintain the interpretability of black-box models is evident. One aspect uses local explanations of the model in the vicinity of an observation. Local explanations approximate the linear variable importance to the model. Our contribution is to assess explanations by examining the support by varying the contributions with a radial tour. First, a global view visualizes approximations of the data and explanation spaces side-by-side, using dynamic interaction to compare and contrast and, identify primary and comparison observations of interest. The normalized linear importance from the explanation of the primary observation becomes the feature of interest to further explore with radial tour. The variable sensitivity to the structure identified in the explanation is explored by the tours.

>>>>

<!-- Paper structure -->
The remainder of this paper is organized as follows. The following section, [Local explanation statistics](#sec:explanations), covers the background of the local explanation, SHAP, and the traditional visuals produced from it. [Tours and the radial tour](#sec:tour) digs deeper into these animations of continuous linear projections. The section [Application Design](#sec:applicationdesign) discusses the visual layouts, how they facilitate analysis, data preprocessing, and package infrastructure. The section [Case Studies](#sec:casestudies) illustrates several applications of this method. We conclude with a [Discussion](#sec:cheemdiscussion) of the insights we draw from classification and regression tasks.

@@

<!-- Uses of local explanations -->
These instance-level explanations are used in various ways depending on the data. In images, saliency maps overlay or offset a heatmap indicating necessary pixels [@simonyan_deep_2014]. For instance, snow may be highlighted when distinguishing if a picture contains a wolf or husky. In text analysis, word-level contextual sentiment analysis can be used to highlight the sentiment and magnitude of influential words [@vanni_textual_2018]. In the case of numeric regression, they are used to explain variable additive contributions from the model intercept to the observation's prediction [@ribeiro_why_2016].

@@

<!-- Illustration -->
Figure \@ref(fig:shapdistrbd) shows the SHAP values of these players. Panel a) shows these players receive a sizable difference in wages. Panel b) shows the underlying distribution of the SHAP attributions while permuting the explanatory variables, with the medians being the SHAP values. In the light of the player position, the difference in the variable importance makes sense; offense and movement skills are more important for the offensive player, while defensive and power skills are more informative to the model for explaining the prediction of the defensive player. We would likewise expect the profile of variable importance to be unique for star players of other positions, such as goalkeepers or middle fielders. Panel b) shows a simplified break-down plot [@gosiewska_ibreakdown_2019], where a local explanation is used to additively explain the difference from the intercept to the observation's prediction. Such additive approaches will show asymmetry in the variable ordering, so we opt to fix the order to panel a) by decreasing the  sum of the SHAP values.

<!-- Segue -->
In summary, this figure highlights how local explanations bring interpretability to a model, at least in the vicinity of their observations. In this instance, two players with different positions receive different profiles of variable importance to explain the prediction of their wages. In application, we apply _tree SHAP_, a variant of SHAP enjoys a lower computational complexity [@lundberg_consistent_2018]. Tree SHAP only compatible with tree-based models; we illustrate random forests. The following section will use normalized explanations as the starting projection basis to further scrutinize the explanation.

@@

<!-- Manual tour -->
The manual tour [@cook_manual_1997] defines its basis path by manipulating a selected variable's contribution to the basis. A manipulation dimension is appended onto the projection plane, giving a full contribution to the chosen variable. The bases are then selected based on rotating this newly created manipulation space. A crucial feature of the manual tour is that it allows users to control the variable contributions of the basis. Such manipulations can be selected and queued in advance or selected on the spot for human-in-the-loop analysis [@karwowski_international_2006]. However, this navigation is relatively time-consuming due to the vast volume of the display space. It is advisable to use this method to explore the sensitivity of the variable contribution to a previously identified feature of interest. In this case, the projection of the normalized explanations is the feature of interest.

@@

Below we illustrate the two primary displays of the cheem viewer application: the global view and the tour view. Then we cover what we take away from the classification and regression tasks. Lastly, we discuss the preprocessing of the data before application runtime.

@@

<!-- Purpose -->
The global view provides an essential context of all observations and facilitates the exploration of the separability of the data- and attribution-spaces. While the comparison of these spaces is interesting, the global view's purpose is to enable the selection of observations. The local explanation of these points will be explored in more detail.

<!-- Approximations of the spaces, PC1:2 -->
An approximation of these spaces is given as the first two principal components of their respective spaces. Model information, the observed response by its prediction, is also provided. The orientation and magnitude of the variables are inscribed on a unit circle. <!-- Interactions -->Misclassified observations are circled in red if applicable. Linked brushing between the plots and tabular display of select points facilitates exploration of the spaces and the model. A single 2D projection will not encompass all of the structure of higher-dimensional space. However, it is a reasonable summarization given the real task at hand; the selection of observations to explore further.

@@

<!-- Tour animation -->
The radial tour creates a basis path by varying the contribution of a selected variable, fully into and out of a projection frame. Doing so tests an individual variable's sensitivity to the structure identified by the local explanation. The default variable selected has the largest discrepancy between the attribution of primary and comparison observations. The following sections elaborate on the takeaways from applying this approach in classification and regression tasks, respectively. <!-- Segue to classification -->Now that we have introduced the global view and corresponding cheem radial tour, let us discuss the differences between the classification and regression cases.

@@

What information do we glean from using this method on a classification task? Typically we select a misclassified observation compared to a correctly classified point nearby in data space. The initial frame is the linear attribution of that observation's local explanation. By default, the manual tour varies the contribution of the variable with the largest difference between the primary and comparison observation; we can test the sensitivity of each variable to structure identified by the local explanation; we are exploring the support of the explanation, evaluating the support or robustness of the prediction.

```{r classificationcase, echo=F, out.width = "100%", fig.align="center", fig.cap = "Display illustrating the classification case. Plots are  colored on predicted class, and red circles indicate misclassified observations. The radial tour is a 1D projection starting at the normalized tree SHAP values of the primary point. The first frame is the linear-variable importances that best describe the difference from model intercept to this observation's prediction. We probe the support of the variable contributions by selecting a variable to vary the contribution."}
knitr::include_graphics("./figures/app_classification.PNG")
```

@@

In the regression case, the global view can be colored on a statistic to highlight the structure in the explanation space, including residuals, log Mahalanobis distance of data space (a measure of outlyingness), and the correlation of the attribution projection with the observed response. In the radial tour, the horizontal positions are the same, the basis projection of the radial tour. The vertical position is fixed to the observed response variable and residuals in the middle and right panels. Correspondingly, the display changes from univariate density to 2D scatterplot. The basis is still one component (horizontal) independent of the vertical position.

```{r regressioncase, echo=F, out.width = "100%", fig.cap="Display of the regression task. The global view can be colored on the correlation of the attribution projection and observed response. In the tour, the horizontal values are the same as the classification case; the projection through the basis. The vertical position is now mapped to the observed y and residuals."}
knitr::include_graphics("./figures/app_regression.PNG")
```

@@

<!-- Reactive vs exploration interactions -->
The application has several reactive inputs that affect the data used, aesthetic display, and tour manipulation. These reactive inputs make the software flexible and extensible. The application also has more exploratory interactions to help link points in the data and extract other information, not on plot axes.

@@

```{r interactions, echo=F, out.width = "100%", fig.cap = "Illustration of data explorations interactions in the global view. This view has linked brushing of the points where observations selected in one facet are highlighted in the other facets and populate an interactive tabular display below. Tooltips display when hovering over an observation."}
knitr::include_graphics("./figures/app_interactions.PNG")
```

@@

It is vital to mitigate the render time of visuals, especially when users may want to iterate many times. To keep render time low, all computational operations should be prepared before runtime. The work remaining at runtime is solely reacting to inputs and rendering of visuals and tables. Below we discuss the steps and details of the reprocessing.

@@

<!-- Note on time of execution -->
The time to preprocess the data will vary significantly with the model and local explanation. For reference, the FIFA data, 5000 observations of nine explanatory variables, took 2.9 seconds to fit a random forest model of modest hyperparameters. Extracting the tree SHAP values of each observation took 254 seconds combined. PCA and statistics of the variables and attributions took 0.6 seconds. These runtimes were from a non-parallelized R session on a modern laptop, but suffice to say that the bulk of the time will be spent on the local attribution. An increase in model complexity or data dimensionality will quickly become an obstacle. This makes tree SHAP, with its reduced computational complexity, a good candidate to start with. Alternatively, the package __fastshap__ [@greenwell_fastshap_2020] claims extremely low runtimes, which are attributed to fewer calls to the prediction function, partial implementation in C++, and efficient use of logical subsetting.

@@

(ref:casepenguins) Species classification of Palmer penguin data. We select an a chinstrap penguin that is mislabeled as an adelie. By varying the contribution to bill length, we that the explanation does not hold when bill length has a large contribution. The .mp4 animation of this tour can be found at [github.com/nspyrison/cheem_paper/blob/main/figures/case_penguins.mp4](https://github.com/nspyrison/cheem_paper/blob/main/figures/case_penguins.mp4)
```{r casepenguins, echo=F, out.width = "100%", fig.cap = "(ref:casepenguins)"}
knitr::include_graphics("./figures/case_penguins.png")
```

@@

The chocolates dataset consists of 88 observations of 10 nutritional measurements from their labels. Each of which was labeled as being either milk or dark chocolates. We can see if a manufacturer accurately portrays the chocolate with this data. We are curious to see if chocolates that nutritionally look like milk chocolates are labeled as dark chocolates, which may hold a higher market value. We should note that not all chocolates consist wholly of chocolate. The addition of other ingredients will decrease the predictive power of the model nutritional explanatory variable. A random forest model is fit classifying the type of chocolate. We selected a chocolate labeled dark, through predicted to be milk chocolate compared with a chocolate labeled 85% cocoa.

(ref:casechocolates) Chocolates data type classification (milk or dark). We select a chocolate labeled as dark though a random forest model predicts it to be milk chocolate in light of the values on the nutritional label. We vary the contribution of calories from fat. Animated tour can be found at [github.com/nspyrison/cheem_paper/blob/main/figures/case_chocolates.mp4](https://github.com/nspyrison/cheem_paper/blob/main/figures/case_chocolates.mp4).
```{r casechocolates, echo=F, out.width = "100%", fig.cap = "(ref:casechocolates)"}
knitr::include_graphics("./figures/case_chocolates.png")
```

Figure \@ref(fig:casechocolates) similarly shows that attribution-space is more separable than data-space. Interestingly, the class imbalance that we suspected was not observed; there are only six chocolates labeled as dark and predicted as milk, while eight of the inverse case. Calories from fat is the variable with the largest difference in treeshap attribution between these points. In this case, it feels a little bit strange to call the selected observation a misclassification of the model. There are plausible reasons that a manufacturer has incentives to cut corners and label their products different than what they are. This feels more like a measurement theory-related problem. In this case, the candy is being sold as dark chocolate, while nutritional value more closely resembles milk chocolates.

@@

(ref:casefifa) FIFA 2020, regressing log wages [2020 Euros] from aggregations of skill measurements. The primary observation is a star offensive player (L. Messi) compared with a top defensive player (V. van Dijk). The animate radial tour can be found at [github.com/nspyrison/cheem_paper/blob/main/figures/case_fifa.mp4](https://github.com/nspyrison/cheem_paper/blob/main/figures/case_fifa.mp4)
```{r casefifa, echo=F, out.width = "100%", fig.cap = "(ref:casefifa)"}
knitr::include_graphics("./figures/case_fifa.png")
```

With figure \@ref(fig:casefifa), we will test the premise of the local explanation. If we remove reaction and movement skills from the basis, offense skills are almost singularly important for explaining the offensive player. We vary the contribution of offensive skills. Offensive skills are removed in the tour (panel b, frame 3), and Messi
is no longer separated from the group. We also notice that accuracy has rotated into the frame, maintaining some separability.

@@

(ref:caseames) Ames housing 2018 regressing log sales price [2018 USD]. Because the SHAP values are relatively well distributed across the variables, there is a lot of redundant information to explain the gap of a prediction. This case may not be ideal for the cheem methodology, though we did find a near singular frame in the manual tour not, something we came looking for, but certainly, an exciting feature to find. The corresponding animation is at [github.com/nspyrison/cheem_paper/blob/main/figures/case_ames2018.mp4](https://github.com/nspyrison/cheem_paper/blob/main/figures/case_ames2018.mp4)
```{r caseames, echo=F, out.width = "100%", fig.cap = "(ref:caseames)"}
knitr::include_graphics("./figures/case_ames2018.png")
```

@@

The need to maintain the interpretability of black-box models is evident. One aspect uses local explanations of the model in the vicinity of an observation. Local explanations approximate the linear variable importance to the model. Our contribution is to assess explanations by examining the support by varying the contributions with a radial tour. First, a global view visualizes approximations of the data and explanation spaces side-by-side, using dynamic interaction to compare and contrast and identify primary and comparison observations of interest. The normalized linear importance from the explanation of the primary observation becomes the feature of interest to further explore with the radial tour. The tours explore the variable sensitivity to the structure identified in
the explanation.

### 2021-12-29 _paper.tex
-.mp4 of the case studies, - added mp4 url and embelishment to case studies. - need to validate that linkes work.

\caption{Species classification of Palmer penguin data.}\label{fig:casepenguins}
\end{figure}

@@

\caption{Chocolates data type classification (milk or dark).}\label{fig:casechocolates}
\end{figure}

In figure \ref{fig:casechocolates}, we similarly see that attribution space is more separable than data-space. Interestingly, the class imbalance that we suspected was not observed; there are only six chocolates labeled as dark and predicted as milk, while eight of the inverse case. Calories from fat is the variable with the largest difference in treeshap attribution between these points.

@@

\caption{FIFA 2020, regressing log wages [2020 Euros] from aggregations of skill measurements. The primary observation is a star offensive player (L. Messi) compared with a top defensive player (V. van Dijk).}\label{fig:casefifa}
\end{figure}

@@

\caption{Ames housing 2018 regressing log sales price [2018 USD].}\label{fig:caseames}
\end{figure}

>>>>

\caption{Species classification of Palmer penguin data. We select an a chinstrp penguin that is mislabeled as an adlie. By varying the cntribution to bill length we that the explaintion does not hold when bill length has a large contribtuion. The .mp4 animaion of this tour can be found at \href{https://github.com/nspyrison/cheem_paper/blob/main/figures/case_penguins.mp4}{github.com/nspyrison/cheem\_paper/blob/main/figures/case\_penguins.mp4}}\label{fig:casepenguins}
\end{figure}

@@

\caption{Chocolates data type classification (milk or dark). We select a chocolate labeled as dark though a random forest model predicts it to be milk chocolate in light of the values on the nutritional label. We vary the contribution form Calories from Fat. Animated tour can be found at \href{https://github.com/nspyrison/cheem_paper/blob/main/figures/case_chocolates.mp4}{github.com/nspyrison/cheem\_paper/blob/main/figures/case\_chocolates.mp4}.}\label{fig:casechocolates}
\end{figure}

In figure \ref{fig:casechocolates}, we similarly see that attribution space is more separable than data-space. Interestingly, the class imbalance that we suspected was not observed; there are only six chocolates labeled as dark and predicted as milk, while eight of the inverse case. Calories from fat is the variable with the largest difference in treeshap attribution between these points. In this case it feels a little bit strange to call the selected observation a misclassification of the model. There plausible reasons that a manufacturer has incentives to cut corners and label their products different than what they are. This feels more like measurement theory related problem. In this case the candy is being sold as dark chocolate, while nutritional value more closely resemble milk chocolate.

@@

\caption{FIFA 2020, regressing log wages {[}2020 Euros{]} from aggregations of skill measurements. The primary observation is a star offensive player (L. Messi) compared with a top defensive player (V. van Dijk). The animate radial tour can be found at \href{https://github.com/nspyrison/cheem_paper/blob/main/figures/case_fifa.mp4}{github.com/nspyrison/cheem\_paper/blob/main/figures/case\_fifa.mp4}}\label{fig:casefifa}
\end{figure}

@@

\caption{Ames housing 2018 regressing log sales price {[}2018 USD{]}. Because the SHAP values are relatively well distributed accross the variables, there is a lot of redundant information to explain the gap of a prediction. This case may not be ideal for the cheem methodology, though we did find a near singular frame in the manual tour not, something we came looing for, but certainly an interesting feature to find. The corresponding animation is at \href{https://github.com/nspyrison/cheem_paper/blob/main/figures/case_ames2018.mp4}{github.com/nspyrison/cheem\_paper/blob/main/figures/case\_ames2018.mp4}}\label{fig:caseames}
\end{figure}
